Descriptive Complexity for Counting Complexity Classes

### 2018-05-07 LMCS/introduction.tex
[journal] Cambios menores y arreglado error en la demo de sigma2hard
Listo para enviar ...

\smallskip

\noindent{\bf Organisation.} The main terminology used in the paper is given in Section~\ref{sec:preliminaries}. Then the logical framework is introduced in Section~\ref{sec:logic}, and it is used to capture standard counting complexity classes in Section~\ref{sec:complexity}. The structure of $\shp$ is studied in Section~\ref{sec:syntactic}. Section~\ref{sec:beyond} is devoted to define recursion in $\qso$, and to show how to capture classes below $\fp$. 
Finally, we give some concluding remarks in Section~\ref{sec:conclusions}. 
Due to the lack of space, the %complete 
proofs of the results of the paper can be found at 
%a separate appendix that can be downloaded from 
\verb+http://marenas.sitios.ing.uc.cl/ls17.pdf+

>>>>

It is important to mention that this paper is an extension of the conference article \cite{AMR17}. In this version, we have included the complete proofs of all the results in the paper, paying special attention in showing the main techniques used to establish them. Besides, we have simplified some of the terminology used in \cite{AMR17}, with the goal of presenting the main notions studied in the paper in a simple way.

\smallskip
\smallskip

\noindent{\bf Organisation.} The main terminology used in the paper is given in Section~\ref{sec:preliminaries}. Then the logical framework is introduced in Section~\ref{sec:logic}, and it is used to capture standard counting complexity classes in Section~\ref{sec:complexity}. The structure of $\shp$ is studied in Section~\ref{sec:syntactic}. Section~\ref{sec:beyond} is devoted to define recursion in $\qso$, and to show how to capture classes below $\fp$. 
Finally, we give some concluding remarks in Section~\ref{sec:conclusions}.
%Due to the lack of space, the proofs of the results of the paper can be found at a separate appendix that can be downloaded from \verb+http://marenas.sitios.ing.uc.cl/ls17.pdf

### 2018-05-07 LMCS/main.tex
journal 8 mar
journal 23 mar
Paso completo a sección 4.
Pasada sobre la seccion 6 y el resto del paper
Listo para enviar ...

%% mandatory lists of keywords 
\keywords{MANDATORY list of keywords}

@@

@@

\title[Counting]{Descriptive Complexity for Counting Complexity Classes}
\titlecomment{{\lsuper*}OPTIONAL comment concerning the title, \eg, 
  if a variant or an extended abstract of the paper has appeared elsewhere.}

\author[M.~Arenas]{Marcelo Arenas}	%required
\address{PUC Chile}	%required
\email{marenas@ing.puc.cl}  %optional
%\thanks{thanks 1, optional.}	%optional

\author[M.~Munoz]{Martin Mu\~noz}	%optional
\address{PUC Chile}	%optional
\email{mmunos@uc.cl}  %optional
%\thanks{thanks 2, optional.}	%optional

\author[C.~Riveros]{Cristian Riveros}	%optional
\address{PUC Chile}	%optional
\email{cristian.riveros@uc.cl}  %optional
%\thanks{thanks 3, optional.}	%optional

@@

\subsection{Extending $\qso$ to capture non-counting classes} \label{sec:extentions}
\input{extentions}

@@

\begin{thebibliography}{10}

\end{thebibliography}

>>>>

%% mandatory lists of keywords 
%\keywords{MANDATORY list of keywords}

@@

%\allowdisplaybreaks

@@

\title[Counting]{Descriptive Complexity for Counting Complexity Classes}
%\titlecomment{{\lsuper*}OPTIONAL comment concerning the title, \eg, 
%  if a variant or an extended abstract of the paper has appeared elsewhere.}

\author[M.~Arenas]{Marcelo Arenas}	%required
\address{Pontificia Universidad Cat\'olica de Chile}	%required
\email{marenas@ing.puc.cl}  %optional
%\thanks{thanks 1, optional.}	%optional

\author[M.~Munoz]{Martin Mu\~noz}	%optional
\address{Pontificia Universidad Cat\'olica de Chile}	%optional
\email{mmunos@uc.cl}  %optional
%\thanks{thanks 2, optional.}	%optional

\author[C.~Riveros]{Cristian Riveros}	%optional
\address{Pontificia Universidad Cat\'olica de Chile}	%optional
\email{cristian.riveros@uc.cl}  %optional
%\thanks{thanks 3, optional.}	%optional

@@

\subsection{Extending $\qso$ to capture classes beyond counting} \label{sec:extentions}
\input{extentions}

@@

\bibliographystyle{plain}
\bibliography{biblio}
